---
title: "NEJM"
author: "Mishek Thapa"
output: pdf_document
header-includes:
- \usepackage{booktabs}
---

There were a few discrepancies. In table 4, there is one more patient included in the dataset than in the paper. The wilcoxin test was mentioned in the paper to get the confidence intervals for table 4's difference in percentage. However, it was not properly clarified how exactly they calculated it. Thus, there is a discrepancy in the confidence intervals for that difference in proportions. (Since the upper and lower bounds of the confidence intervals are essentially at the same value, the difference in percentage was not included).  Overall, documentation could have been improved in that part of the analysis.  


# Table 2

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
```

```{r}
library(tidyverse)
library(dplyr)
library(tidyr)
library(knitr)
library(memisc)
library(qwraps2)
library(survival)
```

```{r}
dig <- read_csv("dig.csv")
options(qwraps2_markup = "markdown")
```



```{r, results='asis'}
#code applied from: https://cran.r-project.org/web/packages/qwraps2/vignettes/summary-statistics.html

#edited the n_perc0 function
get_p <- function (x, digits = getOption("qwraps2_frmt_digits", 1), na_rm = TRUE, 
  show_denom = "never", show_symbol = TRUE, markup = getOption("qwraps2_markup", 
    "latex")) 
{
  d <- sum(!is.na(x))
  n <- sum(x, na.rm = na_rm)
  p <- frmt(100 * n/d, digits)
  if (show_denom == "never") {
    rtn <- paste0("", p)
  }
  if (!show_symbol) {
    rtn <- gsub("%", "", rtn)
  }
  if (markup == "latex") {
    rtn <- gsub("%", "\\\\%", rtn)
  }
  return(rtn)
}




our_summary1 <-
  list("-" =
         list("Age (yr) — mean ± SD"                = ~ qwraps2::mean_sd(AGE, digits = 1),
              "Ejection fraction — mean ± SD"       = ~ qwraps2::mean_sd(EJF_PER, digits = 1),
              "Median duration of CHF — mo" = ~ median(CHFDUR, na.rm = T, digits = 1)),
       "% of patients" =
         list("Female sex" = ~ get_p(SEX == 2),
              "Nonwhite race"  = ~ get_p(RACE == 2),
              "Age>70 yr"  = ~ get_p(AGE > 70)),
       "Method of assessing ejection fraction:" = 
         list( "Radionuclide ventriculography" = ~ get_p(EJFMETH == 1),
               "Two-dimensional echocardiography" = ~ get_p(EJFMETH == 3),
               "Contrast angiography"= ~ get_p(EJFMETH == 2)),
       "-" = list("Cardiothoracic ratio>0.55" =~ get_p(CHESTX > 0.55)),
       "NYHA class" = list("I" =~ get_p(FUNCTCLS == 1),
                           "II" =~ get_p(FUNCTCLS == 2),
                           "III" =~ get_p(FUNCTCLS == 3),
                           "IV"=~ get_p(FUNCTCLS == 4)
                           ),
       "No. of signs or symptoms of CHF†" = list("0" =~ get_p(NSYM == 0),
                                                 "1" =~  get_p(NSYM == 1),
                                                 "2" =~ get_p(NSYM == 2), 
                                                 "3" =~ get_p(NSYM == 3),
                                                 "4+" =~ get_p(NSYM >3)),
       "Medical history" = list("Previous myocardial infarction" =~ get_p(PREVMI == 1),
                                "Current angina" =~ get_p(ANGINA == 1), 
                                "Diabetes" =~ get_p(DIABETES == 1),
                                "Hypertension" =~ get_p(HYPERTEN == 1)),
       "-" = list("Previous digoxin use" =~ get_p(DIGUSE == 1)),
       "Primary Cause of Ischemia" = list( "Ischemic" =~ get_p(CHFETIOL == 1),
                                           "Nonischemic" =~ get_p(CHFETIOL != 1),
                                           "Nonischemic: idiopathic" =~ get_p(CHFETIOL == 4),
                                           "Nonischemic: hypertensive" =~ get_p(CHFETIOL == 2),
                                           "Nonischemic: other" =~ get_p(CHFETIOL %in% c(3,5,6))),
       "Concomitant medications" = list("Diuretics"  =~ get_p(DIURET == 1 | DIURETK == 1),
                                        "Ace Inhibitors"  =~ get_p(ACEINHIB == 1),
                                        "Nitrates"  =~ get_p(NITRATES == 1),
                                        "Other Vasodilators"  =~ get_p(VASOD == 1)),
       "Daily dose of study medication prescribed" = list("0.125 mg" =~ get_p(DIGDOSE == 0.125),
                                                          "0.250 mg" =~ get_p(DIGDOSE == 0.25),
                                                          "0.375 mg" =~ get_p(DIGDOSE == 0.375),
                                                          "0.500 mg" =~ get_p(DIGDOSE == 0.5)))

 summary_table(group_by(dig, TRTMT), our_summary1)
```



# Table 2
(Accidentally also did table 2)

```{r,  results='asis'}
our_summary2 <-
  list("-" = list( "ALL" =~ n_perc0(DEATH == 1, digits = 1),
                   "Cardiovascular" =~ n_perc0(REASON %in% c(1:4), digits =1)),
       "-" = list( "Cardiovascular: Worsening Heart Failure" =~ n_perc0(REASON == 1, na_rm = TRUE, digits = 1),
                   "Cardiovascular: Other Cardiac" =~ n_perc0(REASON == 2, na_rm = TRUE, digits = 1),
                   "Cardiovascular: Other Vascular" =~ n_perc0(REASON == 3, na_rm = TRUE, digits = 1),
                   "Cardiovascular: Unknown" =~ n_perc0(REASON == 4, na_rm = TRUE, digits =1),
                   "Noncardiac and non-vascular" =~ n_perc0(REASON == 5, na_rm = TRUE, digits =1)))

tab <-  summary_table(group_by(dig, TRTMT), our_summary2)
 
tab
```


```{r}
#cox models
dig <- dig %>%
  mutate(
    "death1" = case_when(
    REASON == 1 ~ 1,
    TRUE ~ 0),
    "death2" = case_when(
    REASON == 2 ~ 1,
    TRUE ~ 0),
    "death3" = case_when(
    REASON == 3 ~ 1,
    TRUE ~ 0),
    "death4" = case_when(
    REASON == 4 ~ 1,
    TRUE ~ 0),
    "death5" = case_when(
    REASON == 5 ~ 1,
    TRUE ~ 0),
    "cardiodeath" = case_when(
      REASON %in% c(1:4) ~ 1,
      TRUE ~ 0  )
    )


surva = Surv(dig$DEATHDAY, dig$DEATH)

survc = Surv(dig$DEATHDAY, dig$cardiodeath)

surv1=Surv(dig$DEATHDAY, dig$death1)

surv2=Surv(dig$DEATHDAY, dig$death2)

surv3=Surv(dig$DEATHDAY, dig$death3)

surv4=Surv(dig$DEATHDAY, dig$death4)

surv5=Surv(dig$DEATHDAY, dig$death5)


extract_p <- function(mod1){
  HR = exp(mod1$coefficients)
  lb = exp(confint(mod1))[1]
  ub = exp(confint(mod1))[2]
  p = summary(mod1)$coefficients[, 5]
  data.frame(HR, lb, ub, p)
}

mod1 <- coxph(surv1 ~ TRTMT, data = dig)


map_df(list(coxph(surva ~ TRTMT, data = dig),
            coxph(survc ~ TRTMT, data = dig),
            coxph(surv1 ~ TRTMT, data = dig),
            coxph(surv2 ~ TRTMT, data = dig),
            coxph(surv3 ~ TRTMT, data = dig),
            coxph(surv4 ~ TRTMT, data = dig),
            coxph(surv5 ~ TRTMT, data = dig)), ~extract_p(.x)) %>%
  knitr::kable()
```

# Table 4

```{r}


#placebo percentages
dig_p <- dig %>%
  mutate(EJF_i = case_when(between(EJF_PER, 25,45) ~ 1,
                           EJF_PER<25 ~ 0),
         CHR_i = case_when(CHESTX < 0.56 ~ 1,
                           CHESTX > 0.55 ~ 0),
         NYH_i = case_when(FUNCTCLS %in% c(1,2) ~ 0 ,
                           FUNCTCLS %in% c(3,4) ~ 1 ),
         CHF_i = case_when(CHFETIOL == 1 ~ 1,
                           CHFETIOL != 1 ~ 0),
         overall = 1) %>%
  dplyr::select(EJF_i, CHR_i,CHF_i, NYH_i, DIGUSE, TRTMT, REASON, WHF, overall) %>%
  filter(TRTMT == 0) %>%
  pivot_longer(cols = c(EJF_i, CHR_i,CHF_i, NYH_i, DIGUSE, overall),
               names_to = "Variable",
               values_to = "Value") %>%
  group_by(Variable, Value) %>%
  summarise(n = n(),
            val = sum(REASON == 1 | WHF == 1, na.rm = TRUE)) %>%
  mutate(prop = round(val/n *100,1), 
         Variable = factor(Variable, levels = c("EJF_i",  "DIGUSE","CHF_i", "CHR_i", "NYH_i", "overall"),
                           labels = c("Ejection Frac.",
                                      "Previous Use of Dig",
                                      "Cause of Heart Failure",
                                      "Cardiothor. ratio",
                                      "NYHA Class",
                                      "Study Population"))) %>%
  arrange(Variable) %>%
  filter(!is.na(Value))%>%
  rename(n = "Placebo_Denom",
         val = "Placebo_Nume",
         prop = "Placebo_Prop")

#treatment percentages
dig_t <- dig %>%
  mutate(EJF_i = case_when(between(EJF_PER, 25,45) ~ 1,
                           EJF_PER<25 ~ 0),
         CHR_i = case_when(CHESTX < 0.56 ~ 1,
                           CHESTX > 0.55 ~ 0),
         NYH_i = case_when(FUNCTCLS %in% c(1,2) ~ 0 ,
                           FUNCTCLS %in% c(3,4) ~ 1 ),
         CHF_i = case_when(CHFETIOL == 1 ~ 1,
                           CHFETIOL != 1 ~ 0),
         overall = 1) %>%
  dplyr::select(EJF_i, CHR_i,CHF_i, NYH_i, DIGUSE, TRTMT, REASON, WHF, overall) %>%
  filter(TRTMT == 1) %>%
  pivot_longer(cols = c(EJF_i, CHR_i,CHF_i, NYH_i, DIGUSE, overall),
               names_to = "Variable",
               values_to = "Value") %>%
  group_by(Variable, Value) %>%
  summarise(n = n(),
            val = sum(REASON == 1 | WHF == 1, na.rm = TRUE)) %>%
  mutate(prop = round(val/n *100,1), 
         Variable = factor(Variable, levels = c("EJF_i",  "DIGUSE","CHF_i", "CHR_i", "NYH_i", "overall"),
                           labels = c("Ejection Frac.",
                                      "Previous Use of Dig",
                                      "Cause of Heart Failure",
                                      "Cardiothor. ratio",
                                      "NYHA Class",
                                      "Study Population"))) %>%
  arrange(Variable) %>%
  filter(!is.na(Value)) %>%
  rename(n = "Dig_Denom",
         val = "Dig_Num",
         prop = "Digoxin_Prop")

joined_df <- left_join(dig_t, dig_p) 

```


```{r}
wilcox_df <- joined_df %>%
  pivot_longer(cols = c("Placebo_Prop", "Digoxin_Prop"),
               names_to = "Treatment",
               values_to = "Percentage") %>%
  group_by(Variable, Value) %>%
  summarise(low=wilcox.test(Percentage~Treatment, conf.int = TRUE)$conf.int[1],
            high=wilcox.test(Percentage~Treatment,  conf.int = TRUE)$conf.int[1])
  


dig1 <-  dig %>% filter(between(EJF_PER, 25,45))
surv1=Surv(dig1$DWHFDAYS, dig1$DWHF)

dig2 <-  dig %>% filter(between(EJF_PER, 0,25))
surv2=Surv(dig2$DWHFDAYS, dig2$DWHF)

dig3 <-  dig %>% filter(DIGUSE==1)
surv3=Surv(dig3$DWHFDAYS, dig3$DWHF)

dig4 <-  dig %>% filter(DIGUSE==0)
surv4=Surv(dig4$DWHFDAYS, dig4$DWHF)

dig5 <-  dig %>% filter(CHFETIOL==1)
surv5=Surv(dig5$DWHFDAYS, dig5$DWHF)

dig6 <-  dig %>% filter(CHFETIOL!=1)
surv6=Surv(dig6$DWHFDAYS, dig6$DWHF)

dig7 <-  dig %>% filter(CHESTX < 0.56)
surv7=Surv(dig7$DWHFDAYS, dig7$DWHF)

dig8 <-  dig %>% filter(CHESTX > 0.55)
surv8=Surv(dig8$DWHFDAYS, dig8$DWHF)

dig9 <-  dig %>% filter(FUNCTCLS %in% c(1,2))
surv9=Surv(dig9$DWHFDAYS, dig9$DWHF)

dig10 <-  dig %>% filter(FUNCTCLS %in% c(3,4))
surv10=Surv(dig10$DWHFDAYS, dig10$DWHF)

surv11=Surv(dig$DWHFDAYS, dig$DWHF)


joined_df  %>% dplyr::select(-Value) %>% knitr::kable(caption = "T4: Percentages")
wilcox_df %>% dplyr::select(-Value) %>%   knitr::kable(caption = "T4: Wilcox Tests")

map_df(list(coxph(surv1 ~ TRTMT, data = dig1),
            coxph(surv2 ~ TRTMT, data = dig2),
            coxph(surv3 ~ TRTMT, data = dig3),
            coxph(surv4 ~ TRTMT, data = dig4),
            coxph(surv5 ~ TRTMT, data = dig5),
            coxph(surv6 ~ TRTMT, data = dig6),
            coxph(surv7 ~ TRTMT, data = dig7),
            coxph(surv8 ~ TRTMT, data = dig8),
            coxph(surv9 ~ TRTMT, data = dig9),
            coxph(surv10 ~ TRTMT, data = dig10),
            coxph(surv11 ~ TRTMT, data = dig)), ~extract_p(.x)) %>%
  knitr::kable(caption = "T4: Cox Models")
  

```














